Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-13 docs/ms.tex
update ms.tex

The procedure of our simulation is that, first we generated N{*}NP
unlensed galaxies' elliprticity from the ``true'' $P(\epsilon_{0})$, and
asign these galaxies into NP patches equally. So each patch has N galaxies. Second
we generate NP true reduced shears, and asign them to each patch, and
then shear the unlensed galaxies using formula (4).

>>>>

The procedure of our simulation is as following. First we generated N$\times$NP
unlensed galaxies' elliprticity from the ``true'' $P(\epsilon_{0})$, and
asign these galaxies into NP patches equally. So each patch has N galaxies. Then
we generate NP true reduced shears, and asign them to each patch, and
then shear the unlensed galaxies using formula (4).
